### 2018-01-12 derivations.tex
lots of fixes, finished falloff blending section & added PLOG / Cheb kf derivs

\section{Governing equations}
\subsection{State variables}
The state vector for this derivation consists of the temperature, a thermodynamic parameter (pressure or volume) and the amount of moles of all species except the last in the model:

@@

\subsection{Pressure-dependent reactions}

In addition to the falloff approach given previously, two additional formulations can be used to describe the pressure dependence of reactions that do not follow the modification factor $c_i$ approach.
The first involves logarithmic interpolation between Arrhenius rates at two pressures~\cite{chemkin:2012,Goodwin:2015aa}, each evaluated using \cref{e:arrhenius}:
\begin{align}
k_1 (T) &= A_1 T^{\beta_1} \exp \left( -\frac{T_{a, 1}}{T} \right) \text{ at } P_1 \text{ and} \label{e:plog_k1} \\
k_2 (T) &= A_2 T^{\beta_2} \exp \left( -\frac{T_{a, 2}}{T} \right) \text{ at } P_2 \;, \label{e:plog_k2}
\end{align}
where the Arrhenius coefficients are given for each pressure $p_1$ and $p_2$.
Then, the reaction rate coefficient at a particular pressure $p$ between $p_1$ and $p_2$ can be determined through logarithmic interpolation:
\begin{equation}
\log{\left ({k_f}_{i} \right )} = \frac{\left(- \log{\left (k_{1} \right )} + \log{\left (k_{2} \right )}\right) \left(- \log{\left (P_{1} \right )} + \log{\left (P \right )}\right)}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} + \log{\left (k_{1} \right )}
\end{equation}

In addition, the pressure dependence of a reaction can be expressed through a bivariate Chebyshev polynomial fit~\cite{Venkatesh:1997hv,Venkatesh:1997ik,Venkatesh:2000gj,chemkin:2012,Goodwin:2015aa}:
\begin{equation}
\log_{10} k_f (T, p) = \sum_{i = 1}^{N_T} \sum_{j = 1}^{N_p} \eta_{ij} \phi_i (\tilde{T}) \phi_j \left(\tilde{p}\right) \label{e:cheb} \;,
\end{equation}
where $\eta_{ij}$ is the coefficient corresponding to the grid points $i$ and $j$, $N_T$ and $N_p$ are the numbers of grid points for temperature and pressure, respectively, and $\phi_n$ is the Chebyshev polynomial of the first kind of degree $n - 1$ typically expressed as
\begin{equation}
\phi_n (x) = \mathcal{T}_{n-1} (x) = \cos \left( (n - 1) \arccos (x) \right) \quad \text{for } |x| \leq 1 \;.
\end{equation}
The reduced temperature $\tilde{T}$ and pressure $\tilde{p}$ are given by
\begin{align}
\tilde{T} &\equiv \frac{2 T^{-1} - T^{-1}_{\min} - T^{-1}_{\max}}{T^{-1}_{\max} - T^{-1}_{\min}} \quad\text{and} \\
\tilde{p} &\equiv \frac{2\log_{10} p - \log_{10} p_{\min} - \log_{10} p_{\max}}{\log_{10} p_{\max} - \log_{10} p_{\min}} \;,
\end{align}
where $T_{\min} \leq T \leq T_{\max}$ and $p_{\min} \leq p \leq p_{\max}$ describe the ranges of validity for temperature and pressure.

@@

\subsection{Rate of progress derivatives}
\subsubsection{Temperature derivative}
Next, the rate of progress derivatives are evaluated, first with respect to temperature:
\begin{equation}
 \frac{\partial R }{\partial T }_{i} = \frac{\partial}{\partial T}\left({k_f}_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right)
\end{equation}
the derivative of the forward reaction rate coefficient is:
\begin{equation}
 \label{e:dkf_dt}
 \frac{\text{d} {k_f} }{\text{d} T }_{i} = \frac{{k_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)
\end{equation}
While evaluating derivatives for the Jacobian, it is important to expand terms---e.g., concentration, rate of production, etc.---related to the last species to obtain the correct derivative, in this case using \cref{e:last_spec_conc}:
\begin{equation}
 {R_f} = \left(\left(- \sum_{k=1}^{-1 + \ns} [C]_{k} + \frac{P}{T \Ru}\right)^{\nu^{\prime}_{\ns,i}}\right) {k_f}_{i} \prod_{k=1}^{-1 + \ns} [C]_{k}^{\nu^{\prime}_{k,i}}
\end{equation}
The derivative of a species concentration with respect to temperature is zero for both \conp~and \conv:
\begin{align}
 \frac{\partial [C]_{k}}{\partial T} &= \frac{\partial}{\partial T} \left(\frac{n_k}{V}\right), \quad \left\{k \ne \ns\right\} \nonumber \\
				     &= 0
\end{align}
as the volume is either constant (\conp) or a state variable and a function of time only (\conv).
Hence, the full derivative of the forward rate of progress is:
\begin{equation}
 \label{e:dropfdt_1}
 \frac{\partial {R_f} }{\partial T }_{i} = \frac{\text{d} {k_f} }{\text{d} T }_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}} - \frac{[C] \nu^{\prime}_{\ns,i}}{T} [C]_{\ns}^{\nu^{\prime}_{\ns,i} - 1} {k_f}_{i} \prod_{k=1}^{-1 + \ns} [C]_{k}^{\nu^{\prime}_{k,i}}
\end{equation}
By defining a temporary variable (for species $l = \left\{j, \ns\right\}$) $S^{\prime}_{l}$:
\begin{equation}
 \label{e:s_temp}
 S^{\prime}_{l} = \nu^{\prime}_{l,i} [C]_{l}^{\nu^{\prime}_{l,i} - 1} \prod_{\substack{1 \leq l \leq l - 1\\l + 1 \leq l \leq \ns}} [C]_{l}^{\nu^{\prime}_{l,i}}
\end{equation}
and using~\cref{e:dkf_dt}, \cref{e:dropfdt_1} can be simplified to:
\begin{equation}
 \label{e:dropf_dt}
 \frac{\partial {R_f} }{\partial T }_{i} = - \frac{[C] S^{\prime}_{\ns}}{T} {k_f}_{i} + \frac{{R_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)
\end{equation}

Starting from~\cref{e:ropr} and applying the same expansion of the last species' concentration as previously, the temperature derivative of the reverse rate of progress is:
\begin{equation}
 \frac{\partial {R_r} }{\partial T }_{i} = \frac{\text{d} {k_r} }{\text{d} T }_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime\prime}_{k,i}} - \frac{[C] \nu^{\prime\prime}_{\ns,i}}{T} [C]_{\ns}^{\nu^{\prime\prime}_{\ns,i} - 1} {k_f}_{i} \prod_{k=1}^{-1 + \ns} [C]_{k}^{\nu^{\prime\prime}_{k,i}}
\end{equation}
Next, \cref{e:kr} is considered to obtain the temperature derivative of the non-explicit reversible reaction rate coefficient:
\begin{equation}
 \frac{\text{d} {k_r} }{\text{d} T }_{i} = \left(- \frac{1}{{K_c}_{i}} \frac{\text{d} {K_c} }{\text{d} T }_{i} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {k_r}_{i}
\end{equation}
The temperature derivative of the equilibrium constant is:
\begin{equation}
 \frac{\text{d} {K_c} }{\text{d} T }_{i} = {K_c}_{i} \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} \;,
\end{equation}
with:
\begin{equation}
 \frac{\text{d} B }{\text{d} T }_{k} = T \left(T \left(\frac{T a_{k,4}}{5} + \frac{a_{k,3}}{4}\right) + \frac{a_{k,2}}{3}\right) + \frac{a_{k,1}}{2} + \frac{1}{T} \left(a_{k,0} - 1 + \frac{a_{k,5}}{T}\right)
\end{equation}
giving:
\begin{equation}
\label{e:dkr_dt}
\frac{\text{d} {k_r} }{\text{d} T }_{i} = \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {k_r}_{i} \;,
\end{equation}
and using an temporary value $S^{\prime\prime}_{\ns}$---defined analagously to \cref{e:s_temp} for the reverse direction---we obtain:
\begin{equation}
\label{e:dropr_dt}
\frac{\partial {R_r} }{\partial T }_{i} = \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_r}_{i} - \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_r}_{i}
\end{equation}

Finally, combining~\cref{e:dropf_dt,e:dropr_dt} gives the total temperature derivative of the net rate of progress:
\begin{align}
 \label{e:drop_dt}
 \frac{\partial R }{\partial T }_{i} =& \frac{{R_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right) - \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_r}_{i} \nonumber \\
				      &\qquad + \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_r}_{i} - \frac{[C] S^{\prime}_{\ns}}{T} {k_f}_{i}
\end{align}
\subsubsection{Molar derivative}
\label{s:rop_molar}
The derivative of the forward rate of progress with respect to the amount of moles of a species $j$ is:
\begin{equation}
 \frac{d}{d n_{k}} {R_{f_i}} = \left(\frac{\partial}{\partial n_{j}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right) {k_f}_{i} \;.
\end{equation}
The derivative of a species concentration with respect to moles of a species $j$ is given as:
\begin{equation}
 \frac{\partial [C_k]}{\partial n_j} =
 \begin{dcases}
 \frac{\delta_{j k}}{V} & k \ne \ns \\
 -\frac{1}{V} & k = \ns
 \end{dcases}
\end{equation}
Or put succinctly:
\begin{equation}
\label{e:dck_dnj}
\frac{\partial [C_k]}{\partial n_j} = \frac{\delta_{j k} - \delta_{\ns k}}{V} \;.
\end{equation}
Using~\cref{e:dck_dnj} the molar derivative of the forward rate of progress is found as:
\begin{equation}
 \frac{\partial {R_f}_{i} }{\partial {n_j} } = {k_f}_{i} \sum_{k=1}^{\ns} \left(- \frac{\delta_{\ns k}}{V} + \frac{\delta_{j k}}{V}\right) \nu^{\prime}_{k,i} [C]_{k}^{\nu^{\prime}_{k,i} - 1} \prod_{\substack{1 \leq l \leq k - 1\\k + 1 \leq l \leq \ns}} [C]_{l}^{\nu^{\prime}_{l,i}}
\end{equation}
with the same temporary variables $S^{\prime}_{j}$ and $S^{\prime}_{\ns}$ as defined previously, this can be simplified to:
\begin{equation}
 \label{e:dropf_dnj}
 \frac{\partial {R_f}_{i} }{\partial {n_j} } = \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}
and by the same process, the reverse rate of progress derivative is found to be:
\begin{equation}
 \label{e:dropr_dnj}
 \frac{\partial {R_r}_{i} }{\partial {n_j} } = \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right)
\end{equation}
and the net rate of progress molar derivative:
\begin{equation}
 \frac{\partial R_{i} }{\partial {n_j} } = - \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right) + \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}

\subsubsection{Parameter derivatives}
The derivatives of the forward and reverse rates of progress with respect to the volume (\conp) or pressure (\conv) largely follow the same format of the previous sections.
First, the derivative of the concentration of a species $k$ with respect to the parameter is:

\begin{subequations}
 \begin{align}
 \lhs{dck}{\frac{\partial [C] }{\partial V }_{k}} &=
  \begin{dcases}
  \rhs{dck}{\frac{[C]_{k}}{V}} & \mathcond{dck}{k \ne \ns} \\
  \rhs{dck}{\frac{1}{V} \sum_{k=1}^{-1 + \ns} [C]_{k}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconp}
 \lhs{dck}{\frac{\partial [C]_{k} }{\partial P }} &=
 \begin{dcases} \\
   \rhs{dck}{0} & \mathcond{dck}{k \ne \ns} \\
   \rhs{dck}{\frac{1}{T \Ru}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconv}
 \end{align}
\end{subequations}

Following the outline of~\cref{s:rop_molar}, the forward rate of progress derivatives are:
\begin{subequations}
 \begin{align}
  \lhs{dri_de}{\frac{\partial {R_f}_{i} }{\partial V }} &= \rhs{dri_de}{\frac{[C] S^{\prime}_{\ns}}{V} {k_f}_{i} - \frac{{R_f}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}}&\cond{dri_de}{\dconp}\\
  \lhs{dri_de}{\frac{\partial {R_f}_{i} }{\partial P }} &= \rhs{dri_de}{\frac{S^{\prime}_{\ns} {k_f}_{i}}{T \Ru}}&\cond{dri_de}{\dconv}
 \end{align}
\end{subequations}
and similarly, the reverse rate of progress derivatives:
\begin{subequations}
 \begin{align}
  \lhs{dri_de}{\frac{\partial {R_r}_{i} }{\partial V }} &= \rhs{dri_de}{\frac{[C] S^{\prime\prime}_{\ns}}{V} {k_r}_{i} - \frac{{R_r}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}}&\cond{dri_de}{\dconp}\\
  \lhs{dri_de}{\frac{\partial {R_r}_{i} }{\partial P }} &= \rhs{dri_de}{\frac{S^{\prime\prime}_{\ns} {k_r}_{i}}{T \Ru}}&\cond{dri_de}{\dconv}
 \end{align}
\end{subequations}
giving finally:
\begin{subequations}
 \label{e:dropi_de}
 % linebreak and parenthesis sizing:
 % https://tex.stackexchange.com/questions/49890/linebreak-between-left-and-right/49895
 \begin{align}
  \frac{\partial {R}_{i} }{\partial V } &= \frac{1}{V}\left(\vphantom{{R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}} [C]\left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right) + \right.& \nonumber\\
  &\left. \quad\left({R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i} - {R_f}_{i} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}\right) \right)&\dconp\\
  \frac{\partial {R}_{i} }{\partial P } &= \frac{1}{T \Ru} \left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right)&\dconv
 \end{align}
\end{subequations}

>>>>

\section{Governing equations}
\subsection{State variables}
The state vector for this derivation consists of the temperature, a thermodynamic state parameter (pressure or volume) and the amount of moles of all species except the last in the model:

@@

\subsection{Pressure-dependent reactions}
\label{s:pdep}

In addition to the falloff approach given previously, two additional formulations can be used to describe the pressure dependence of reactions that do not follow the modification factor $c_i$ approach.
The first involves logarithmic interpolation between Arrhenius rates at two pressures~\cite{chemkin:2012,Goodwin:2015aa} (often termed P-Log reactions), each evaluated using~\cref{e:arrhenius}:
\begin{align}
k_1 (T) &= A_1 T^{\beta_1} \exp \left( -\frac{T_{a, 1}}{T} \right) \text{ at } P_1 \text{ and} \label{e:plog_k1} \\
k_2 (T) &= A_2 T^{\beta_2} \exp \left( -\frac{T_{a, 2}}{T} \right) \text{ at } P_2 \;, \label{e:plog_k2}
\end{align}
where the Arrhenius coefficients are given for each pressure $p_1$ and $p_2$.
Then, the reaction rate coefficient at a particular pressure $p$ between $p_1$ and $p_2$ can be determined through logarithmic interpolation:
\begin{equation}
\label{e:kf_plog}
\log{\left ({k_f}_{i} \right )} = \frac{\left(- \log{\left (k_{1} \right )} + \log{\left (k_{2} \right )}\right) \left(- \log{\left (P_{1} \right )} + \log{\left (P \right )}\right)}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} + \log{\left (k_{1} \right )}
\end{equation}

In addition, the pressure dependence of a reaction can be expressed through a bivariate Chebyshev polynomial fit~\cite{Venkatesh:1997hv,Venkatesh:1997ik,Venkatesh:2000gj,chemkin:2012,Goodwin:2015aa}:
\begin{equation}
\label{e:kf_cheb}
\log_{10} k_f (T, p) = \sum_{i = 1}^{N_T} \sum_{j = 1}^{N_p} \eta_{ij} \phi_i (\tilde{T}) \phi_j \left(\tilde{p}\right) \;,
\end{equation}
where $\eta_{ij}$ is the coefficient corresponding to the grid points $i$ and $j$, $N_T$ and $N_p$ are the numbers of grid points for temperature and pressure, respectively, and $\phi_n$ is the Chebyshev polynomial of the first kind of degree $n - 1$ typically expressed as
\begin{equation}
\phi_n (x) = \mathcal{T}_{n-1} (x) = \cos \left( (n - 1) \arccos (x) \right) \quad \text{for } |x| \leq 1 \;.
\end{equation}
The reduced temperature $\tilde{T}$ and pressure $\tilde{p}$ are given by
\begin{align}
\tilde{T} &\equiv \frac{2 T^{-1} - T^{-1}_{\min} - T^{-1}_{\max}}{T^{-1}_{\max} - T^{-1}_{\min}} \quad\text{and} \\
\tilde{p} &\equiv \frac{2\log_{10} p - \log_{10} p_{\min} - \log_{10} p_{\max}}{\log_{10} p_{\max} - \log_{10} p_{\min}} \;,
\end{align}
where $T_{\min} \leq T \leq T_{\max}$ and $p_{\min} \leq p \leq p_{\max}$ describe the ranges of validity for temperature and pressure.

@@

\subsection{Rate of progress derivatives}
\subsubsection{Temperature derivative}
\label{s:dri_dt}
Next, the rate of progress derivatives are evaluated, first with respect to temperature:
\begin{equation}
 \frac{\partial R }{\partial T }_{i} = \frac{\partial}{\partial T}\left({k_f}_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right)
\end{equation}
the derivative of the forward reaction rate coefficient is:
\begin{equation}
 \label{e:dkf_dt}
 \frac{\text{d} {k_f} }{\text{d} T }_{i} = \frac{{k_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)
\end{equation}
While evaluating derivatives for the Jacobian, it is important to expand terms---e.g., concentration, rate of production, etc.---related to the last species to obtain the correct derivative, in this case using \cref{e:last_spec_conc}:
\begin{equation}
 {R_f} = \left(\left(- \sum_{k=1}^{-1 + \ns} [C]_{k} + \frac{P}{T \Ru}\right)^{\nu^{\prime}_{\ns,i}}\right) {k_f}_{i} \prod_{k=1}^{-1 + \ns} [C]_{k}^{\nu^{\prime}_{k,i}}
\end{equation}
The derivative of a species concentration with respect to temperature is zero for both \conp~and \conv:
\begin{align}
 \frac{\partial [C]_{k}}{\partial T} &= \frac{\partial}{\partial T} \left(\frac{n_k}{V}\right), \quad \left\{k \ne \ns\right\} \nonumber \\
				     &= 0
\end{align}
as the volume is either constant (\conp) or a state variable and a function of time only (\conv).
Hence, the full derivative of the forward rate of progress is:
\begin{equation}
 \label{e:dropfdt_1}
 \frac{\partial {R_f} }{\partial T }_{i} = \frac{\text{d} {k_f} }{\text{d} T }_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}} - \frac{[C] \nu^{\prime}_{\ns,i}}{T} [C]_{\ns}^{\nu^{\prime}_{\ns,i} - 1} {k_f}_{i} \prod_{k=1}^{-1 + \ns} [C]_{k}^{\nu^{\prime}_{k,i}}
\end{equation}
By defining a temporary variable $S^{\prime}_{l}$ (for species $l = \left\{j, \ns\right\}$):
\begin{equation}
 \label{e:s_temp}
 S^{\prime}_{l} = \nu^{\prime}_{l,i} [C]_{l}^{\nu^{\prime}_{l,i} - 1} \prod_{\substack{1 \leq l \leq l - 1\\l + 1 \leq l \leq \ns}} [C]_{l}^{\nu^{\prime}_{l,i}}
\end{equation}
and using~\cref{e:dkf_dt}, \cref{e:dropfdt_1} can be simplified to:
\begin{equation}
 \label{e:dropf_dt}
 \frac{\partial {R_f} }{\partial T }_{i} = - \frac{[C] S^{\prime}_{\ns}}{T} {k_f}_{i} + \frac{{R_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)
\end{equation}

Starting from~\cref{e:ropr} and applying the same expansion of the last species' concentration as previously, the temperature derivative of the reverse rate of progress is:
\begin{equation}
 \label{e:droprdt_1}
 \frac{\partial {R_r} }{\partial T }_{i} = \frac{\text{d} {k_r} }{\text{d} T }_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime\prime}_{k,i}} - \frac{[C] \nu^{\prime\prime}_{\ns,i}}{T} [C]_{\ns}^{\nu^{\prime\prime}_{\ns,i} - 1} {k_f}_{i} \prod_{k=1}^{-1 + \ns} [C]_{k}^{\nu^{\prime\prime}_{k,i}}
\end{equation}
Next, \cref{e:kr} is considered to obtain the temperature derivative of the non-explicit reversible reaction rate coefficient:
\begin{equation}
 \frac{\text{d} {k_r} }{\text{d} T }_{i} = \left(- \frac{1}{{K_c}_{i}} \frac{\text{d} {K_c} }{\text{d} T }_{i} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {k_r}_{i}
\end{equation}
The temperature derivative of the equilibrium constant is:
\begin{equation}
 \frac{\text{d} {K_c} }{\text{d} T }_{i} = {K_c}_{i} \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} \;,
\end{equation}
with:
\begin{equation}
 \frac{\text{d} B }{\text{d} T }_{k} = T \left(T \left(\frac{T a_{k,4}}{5} + \frac{a_{k,3}}{4}\right) + \frac{a_{k,2}}{3}\right) + \frac{a_{k,1}}{2} + \frac{1}{T} \left(a_{k,0} - 1 + \frac{a_{k,5}}{T}\right)
\end{equation}
giving:
\begin{equation}
\label{e:dkr_dt}
\frac{\text{d} {k_r} }{\text{d} T }_{i} = \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {k_r}_{i} \;,
\end{equation}
and using an temporary value $S^{\prime\prime}_{\ns}$---defined analagously to \cref{e:s_temp} for the reverse direction---we obtain:
\begin{equation}
\label{e:dropr_dt}
\frac{\partial {R_r} }{\partial T }_{i} = \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_r}_{i} - \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_r}_{i}
\end{equation}

Finally, combining~\cref{e:dropf_dt,e:dropr_dt} gives the total temperature derivative of the net rate of progress:
\begin{align}
 \label{e:drop_dt}
 \frac{\partial R }{\partial T }_{i} =& \frac{{R_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right) - \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_r}_{i} \nonumber \\
				      &\qquad + \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_r}_{i} - \frac{[C] S^{\prime}_{\ns}}{T} {k_f}_{i}
\end{align}
\subsubsection{Molar derivative}
\label{s:dri_dnj}
The derivative of the forward rate of progress with respect to the amount of moles of a species $j$ is:
\begin{equation}
 \frac{d}{d n_{k}} {R_{f_i}} = \left(\frac{\partial}{\partial n_{j}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right) {k_f}_{i} \;.
\end{equation}
The derivative of a species concentration with respect to moles of a species $j$ is given as:
\begin{equation}
 \frac{\partial [C_k]}{\partial n_j} =
 \begin{dcases}
 \frac{\delta_{j k}}{V} & k \ne \ns \\
 -\frac{1}{V} & k = \ns
 \end{dcases}
\end{equation}
Or put succinctly:
\begin{equation}
\label{e:dck_dnj}
\frac{\partial [C_k]}{\partial n_j} = \frac{\delta_{j k} - \delta_{\ns k}}{V} \;.
\end{equation}
Using~\cref{e:dck_dnj} the molar derivative of the forward rate of progress is found as:
\begin{equation}
 \frac{\partial {R_f}_{i} }{\partial {n_j} } = {k_f}_{i} \sum_{k=1}^{\ns} \left(- \frac{\delta_{\ns k}}{V} + \frac{\delta_{j k}}{V}\right) \nu^{\prime}_{k,i} [C]_{k}^{\nu^{\prime}_{k,i} - 1} \prod_{\substack{1 \leq l \leq k - 1\\k + 1 \leq l \leq \ns}} [C]_{l}^{\nu^{\prime}_{l,i}}
\end{equation}
with the same temporary variables $S^{\prime}_{j}$ and $S^{\prime}_{\ns}$ as defined previously, this can be simplified to:
\begin{equation}
 \label{e:dropf_dnj}
 \frac{\partial {R_f}_{i} }{\partial {n_j} } = \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}
and by the same process, the reverse rate of progress derivative is found to be:
\begin{equation}
 \label{e:dropr_dnj}
 \frac{\partial {R_r}_{i} }{\partial {n_j} } = \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right)
\end{equation}
and the net rate of progress molar derivative:
\begin{equation}
 \frac{\partial R_{i} }{\partial {n_j} } = - \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right) + \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}

\subsubsection{State parameter derivatives}
\label{s:dri_de}
The derivatives of the forward and reverse rates of progress with respect to the volume (\conp) or pressure (\conv) largely follow the same format of the previous sections.
First, the derivative of the concentration of a species $k$ with respect to the state parameter is:

\begin{subequations}
 \begin{align}
 \lhs{dck}{\frac{\partial [C] }{\partial V }_{k}} &=
  \begin{dcases}
  \rhs{dck}{\frac{[C]_{k}}{V}} & \mathcond{dck}{k \ne \ns} \\
  \rhs{dck}{\frac{1}{V} \sum_{k=1}^{-1 + \ns} [C]_{k}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconp} \\
 \lhs{dck}{\frac{\partial [C]_{k} }{\partial P }} &=
 \begin{dcases} \\
   \rhs{dck}{\mathindent[s]0} & \mathcond{dck}{k \ne \ns} \\
   \rhs{dck}{\frac{1}{T \Ru}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconv}
 \end{align}
\end{subequations}

Following the outline of~\cref{s:dri_dnj}, the forward rate of progress derivatives are:
\begin{subequations}
 \begin{align}
  \lhs{dri_de}{\frac{\partial {R_f}_{i} }{\partial V }} &= \rhs{dri_de}{\frac{[C] S^{\prime}_{\ns}}{V} {k_f}_{i} - \frac{{R_f}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}}&\cond{dri_de}{\dconp}\\
  \lhs{dri_de}{\frac{\partial {R_f}_{i} }{\partial P }} &= \rhs{dri_de}{\frac{S^{\prime}_{\ns} {k_f}_{i}}{T \Ru}}&\cond{dri_de}{\dconv}
 \end{align}
\end{subequations}
and similarly, the reverse rate of progress derivatives:
\begin{subequations}
 \begin{align}
  \lhs{dri_de}{\frac{\partial {R_r}_{i} }{\partial V }} &= \rhs{dri_de}{\frac{[C] S^{\prime\prime}_{\ns}}{V} {k_r}_{i} - \frac{{R_r}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}}&\cond{dri_de}{\dconp}\\
  \lhs{dri_de}{\frac{\partial {R_r}_{i} }{\partial P }} &= \rhs{dri_de}{\frac{S^{\prime\prime}_{\ns} {k_r}_{i}}{T \Ru}}&\cond{dri_de}{\dconv}
 \end{align}
\end{subequations}
giving finally:
\begin{subequations}
 \label{e:dropi_de}
 \begin{align}
  \lhs{dri_de}{\frac{\partial {R}_{i} }{\partial V }} &= \rhs{dri_de}{\frac{1}{V}\Biggl( [C]\left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right) + } & \nonumber\\
  & \rhs{dri_de}{\mathindent[farth] \left({R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i} - {R_f}_{i} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}\right) \Biggr)}&\cond{dri_de}{\dconp}\\
  \lhs{dri_de}{\frac{\partial {R}_{i} }{\partial P }} &= \rhs{dri_de}{\frac{1}{T \Ru} \left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right)}&\cond{dri_de}{\dconv}
 \end{align}
\end{subequations}
